---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# movmean

<!-- badges: start -->
[![License](http://img.shields.io/badge/license-GPL%20%28%3E=%203%29-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-3.0.html)
<!-- badges: end -->

> 2020年CUG大气科学系   
> R、Python、Julia、Fortran、Rcpp混合编程模板

## Assignment (10 points)

选择任意一个你擅长的语言，在该repository的基础上，编写滑动平均函数，测试通过后github推送给我。

**主要步骤如下：**

1. 登陆github账户，fork此repository
2. git clone 克隆的仓库链接
3. 编写函数，编写R语言接口
4. devtools::load_all()配合browser测试
5. git commit提交到github，__**commit message中写明学号和姓名**__
6. Pull request提交给我

**如何修改remote-url:**
```bash
# change remote url
git remote set-url origin https://github.com/your_username/movmean
git push
```

## Installation

``` r
devtools::install_github("kongdd/movmean")
```

## Benchmarks


```{r}
x = c(NA, 1, 2, 3, 4, 5, Inf)
# answer = c(1, 1.5, 2, 3, 4, 4.5, 5)
r_cpp <- movmean_rcpp(x, halfwin = 1)
# 欲用此版本需安装Julia，Julia版本暂时不能考虑NA, Inf
# r_jl <- movmean_julia(x, halfwin = 1)
```

## Acknowledgements

Keep in mind that this repository is released under a GPL3 license,
which permits commercial use but requires that the source code (of
derivatives) is always open even if hosted as a web service.
